--
title: "Final_Project_Spotify"
author: "Hanif Akhtar"
date: "5/31/2021"
output: 
  html_document: 
    keep_md: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Spotify data analysis

# Introduction

The background underlying of this analysis is to get a better understanding of the behavior of music when listening to songs on Spotify. In this analysis I will explore the feature of a song and its effect to the popularity of a song based on a Spotify data set from the TidyTuesday series. Specifically, there are several subgoals of the analyses: 1) To explore the popular song and genre and their characteristics, and 2) to predict the `track_popularity` of a song based on the features of a song (`danceability`, `energy`, `loudness`, `speechiness`, `acousticness`, `instrumentalness`, `liveness`, `valence`, `tempo`, `duration_ms`) using multiple linear regression analysis. After cleaning the data, I will explore the variables and carefully constructed ggplots to conduct numerical and visual analyses.

## Loading Library and Data
The data used in this project was obtained from the [GitHub TidyTuesday project](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-01-21/spotify_songs.csv).

```{r}
library(tidyverse)
library(DT)
library(psych)
library(car)
library(broom)
spotify <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-01-21/spotify_songs.csv')
```

## Preliminary Exploration and Data Cleaning

```{r}
glimpse(spotify)
```
